Streaming $2$-Center with Outliers in High Dimension

### 2015-04-17 paper.tex
changing euclidean to Euclidean

\begin{abstract}
In this paper, we study the $2$-center streaming problem with $z$ outliers in a general space, which means finding two congruent balls covering all the points except $z$ outliers in a streaming work-space. Before considering this problem, we provide a  $2$-approximation algorithm for $1$-center with $z$ outliers in a general space. Our algorithm for the $2$-center problem uses an update time and working space polynomial in $d$ and sub-linear in $n$ to calculate a $(1.8+\eps)$-approximation solution.
\end{abstract}

>>>>

\begin{abstract}
In this paper, we study the $2$-center streaming problem with $z$ outliers in a Euclidean space, which means finding two congruent balls covering all the points except $z$ outliers in a streaming work-space. Before considering this problem, we provide a  $2$-approximation algorithm for $1$-center with $z$ outliers in a Euclidean space. Our algorithm for the $2$-center problem uses an update time and working space polynomial in $d$ and sub-linear in $n$ to calculate a $(1.8+\eps)$-approximation solution.
\end{abstract}
